%-------------------------
% Resume in Latex
% Author : Trevor White
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\input ulem.sty


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Trevor White} \\ \vspace{2pt}
    Detroit, Michigan \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ {734-552-3120} ~ 
    {\raisebox{-0.2\height}\faEnvelope{ me@trevorallenwhite.com}} ~\\ \vspace{0pt}
    \small \href{http://www.TrevorAllenWhite.com}{\raisebox{-0.2\height}\faLink\ \uline{trevorallenwhite.com}} ~
    \href{https://linkedin.com/in/trevorallenwhite/}{\raisebox{-0.2\height}\faLinkedin\ \uline{linkedin.com/in/trevorallenwhite}} ~
    \href{https://github.com/trevtravtrev}{\raisebox{-0.2\height}\faGithub\ \uline{github.com/trevtravtrev}}
    \vspace{-12pt}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Ford Motor Company}{May 2019 -- Present}
      {Software Engineer, Autonomous Vehicles}{Detroit, Michigan}
      \resumeItemListStart
        \resumeItem{Lead software engineer responsible for architecting and coding high-fidelity future autonomous vehicle prototypes.}
        \resumeItem{Progressed from contract (via ESG Automotive) to direct in just 10 months, quickly earning Level 6, Level 7, and Level 7 HTHD promotions for exceptional performance.}
        \resumeItem{Achieved a 60\% reduction in costs and development time through modular architecture, optimization, and software.}
        \resumeItem{Recognized with 3 Henry Ford Awards, Henry Ford Technology of the Year Runner-Up, and pending patent for AV innovations.}
      \resumeItemListEnd

    \resumeSubheading
      {Viral Social, LLC}{October 2015 -- December 2022}
      {Founder}{Detroit, Michigan}
      \resumeItemListStart
        \resumeItem{Founded a social media automation and growth software startup, serving customers from Fortune 500 companies to Grammy award winning artists.}
        \resumeItem{Led a team of 7 contractors and 100+ social media accounts, amassing over 20 million followers.}
        \resumeItem{Grew annual revenue from zero to six figures without external funding.}
        \resumeItem{Achieved a 95\%+ profit margin with a 75\% reduction in operational costs via software automation.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-14pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Wayne State University}{January 2015 -- December 2018}
      {Bachelor of Science in Computer Science}{Detroit, Michigan}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://www.detroitnews.com/story/business/autos/ford/2021/12/14/ford-autonomous-shuttle-deliver-food-detroit-senior-citizens/6498168001/}{\faLink\ \uline {Ford Autonomous Delivery Vehicle}}} $|$ Python, Linux, OpenCV, Neopixel, Socket, Docker}{December 2021}
            \vspace{-12pt}
          \resumeItemListStart
            \resumeItem{Lead software engineer for the Computer Vision Pedestrian Detection System.}
            \resumeItem{Features a cross-vehicle lightbar that offers pedestrians clear visual movement tracking feedback to cross the road safely.}
            \resumeItem{Autonomously delivered over 10,000 pounds of food to underprivileged senior citizens in Detroit.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{\href{https://www.cnet.com/roadshow/news/argo-ai-third-generation-self-driving-development-car-detroit/}{\faLink\ \uline{Ford Self-Driving Vehicle}}} $|$ Python, Raspberry Pi, PyGame, Protobuf, TCP/IP, Docker}{June 2019}
        \vspace{-12pt}
          \resumeItemListStart
            \resumeItem{Lead software engineer for the Autonomous Audio Communication System.}
            \resumeItem{Enables independent communication with passengers and pedestrians with interior and exterior vehicle-triggered audio.}
            \resumeItem{Deployed in 300+ autonomous prototype vehicles showcasing its robust architecture, scalability, and error handling.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{\href{https://github.com/trevtravtrev/StayAwake}{\faLink\ \uline{Stay Awake App}}} $|$ Python, PyQt5, PyAutoGUI, Pyinstaller, Poetry}{June 2020}
        \vspace{-12pt}
          \resumeItemListStart
            \resumeItem{Developed an open-source, cross-platform application that prevents your computer from going to sleep.}
            \resumeItem{Features a modern, single-button user interface with native system notifications and tray minimization.}
            \resumeItem{Offers easy installation via binary release, Poetry, and requirements.txt.}
            \resumeItem{Highly popular with 20,000+ clones, 1,000+ downloads, and 70+ stars.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{\href{https://github.com/trevtravtrev/CoinSense}{\faLink\ \uline{Coin Sense App}}} $|$ Python, Selenium, Pandas, Tabulate, Threading, Docker, Poetry}{April 2021}
        \vspace{-12pt}
          \resumeItemListStart
            \resumeItem{Created a real-time CLI cryptocurrency portfolio value tracking application.}
            \resumeItem{Supports an unlimited amount of coins, including all BNB and ETH network coins, via a simple settings file.}
            \resumeItem{Ships with effortless setup via Docker, Poetry, and requirements.txt.}
            \resumeItem{Widely utilized with 25,000+ clones and 60+ stars.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------INVOLVEMENT---------------
\section{Additional Experience and Awards}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Head Coach for High School Tennis Team} {(2016 - 2019)} \\
     \textbf{3x Henry Ford Award Winner} {(2019, 2021, 2022)} \\
     \textbf{Henry Ford Technology of the Year Award Runner-Up} {(2019)} \\
     \textbf{Pending Patent for Autonomous V2V Communication (US84517399)} {(2023)} \\
    }}
 \end{itemize}
 \vspace{-15pt}

%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, C, C\#, Javascript, HTML/CSS, SQL, Shell, Bash} \\
     \textbf{Developer Tools}{: VS Code, Pycharm, Visual Studio, Arduino IDE} \\
     \textbf{Technologies}{: Linux, Docker, GitHub, Jira, Trello, CI/CD, Arduino, Raspberry Pi} \\
      \textbf{Libraries/Frameworks}{: OpenCV, PyQt, Requests, Selenium, Pandas, Numpy, Asyncio, Threading, Protobuf, JSON, Socket, FastAPI, Scrapy, Flask, Pillow, PyGame, Kivy, Regex, Os, Poetry, Black, Flake8, Radon, Bandit, Isort, MyPy, .NET } \\
    }}
 \end{itemize}
 \vspace{-16pt}
\end{document}


